Hardware-Accelerated Rendering of Intersecting Volumes using Boolean Operations

### 2013-06-23 paper.tex
Sorted rows in performance table (ref #17)
Fixed names of approaches in table and charts (ref #17)
Removed blurb about stage changes with slicing method (ref #17)

\begin{table}
  \centering
  \begin{tabular}{ l r r r }
    \toprule
    Approach & Macbook & Desktop & Workstation\\
    \midrule
    Boolean AND with masking & 12 & 4 & 37 \\
    Boolean AND with XOR & 12 & 4 & 38 \\
    Slicing & 12 & 3 & 32 \\
    Optimized Slicing & 3 & 3 & 35 \\
    \bottomrule
  \end{tabular}
  \caption{Performance measurements}
  \label{performance-table}
\end{table}

@@

As a baseline the Boolean-based approaches were compared to the existing
view-aligned slicing method from previous work by developing a simple prototype.
Since the slicing method requires significantly more state changes when the
volumes are side-by-side as opposed to when one is in front of the other, it was
particularly important with this method that performance measurements were taken
from a variety of perspectives.

@@

\begin{figure}
\centering
\begin{tikzpicture}
\begin{axis}[
    title=3.0 GHz Intel Pentium 4 with NVIDIA GeForce 8500 GT,
    xlabel=Samples,
    ylabel=Frames Per Second]
\addplot coordinates {
  (100, 4)
  (200, 3)
  (300, 2)
  (400, 1)
  (500, 1)
};
\addlegendentry{Boolean XOR}
\addplot coordinates {
  (100, 4)
  (200, 2)
  (300, 2)
  (400, 1)
  (500, 1)
};
\addlegendentry{Depth-masking}
\addplot coordinates {
  (100, 3)
  (200, 1)
  (300, 1)
  (400, 1)
  (500, 1)
};
\addlegendentry{Slicing (uniforms)}
\addplot coordinates {
  (100, 3)
  (200, 1)
  (300, 1)
  (400, 1)
  (500, 1)
};
\addlegendentry{Slicing (attributes)}
\end{axis}
\end{tikzpicture}
\caption{
Chart showing performance measurements as number of samples varies on an Intel
Pentium 4 system with an NVIDIA GeForce 8500 GT video card.
}
\label{desktop-performance-chart}
\end{figure}

>>>>

\begin{table}
  \centering
  \begin{tabular}{ l r r r }
    \toprule
    Approach & Macbook & Desktop & Workstation\\
    \midrule
    Boolean XOR & 12 & 4 & 38 \\
    Depth-Masking & 12 & 4 & 37 \\
    General Slicing & 12 & 3 & 32 \\
    Optimized Slicing & 3 & 3 & 35 \\
    \bottomrule
  \end{tabular}
  \caption{Performance measurements}
  \label{performance-table}
\end{table}

@@

As a baseline the Boolean-based approaches were compared to the existing
view-aligned slicing method from previous work by developing a simple prototype.

@@

\begin{figure}
\centering
\begin{tikzpicture}
\begin{axis}[
    title=3.0 GHz Intel Pentium 4 with NVIDIA GeForce 8500 GT,
    xlabel=Samples,
    ylabel=Frames Per Second]
\addplot coordinates {
  (100, 4)
  (200, 3)
  (300, 2)
  (400, 1)
  (500, 1)
};
\addlegendentry{Boolean XOR}
\addplot coordinates {
  (100, 4)
  (200, 2)
  (300, 2)
  (400, 1)
  (500, 1)
};
\addlegendentry{Depth-Masking}
\addplot coordinates {
  (100, 3)
  (200, 1)
  (300, 1)
  (400, 1)
  (500, 1)
};
\addlegendentry{General Slicing}
\addplot coordinates {
  (100, 3)
  (200, 1)
  (300, 1)
  (400, 1)
  (500, 1)
};
\addlegendentry{Optimized Slicing}
\end{axis}
\end{tikzpicture}
\caption{
Chart showing performance measurements as number of samples varies on an Intel
Pentium 4 system with an NVIDIA GeForce 8500 GT video card.
}
\label{desktop-performance-chart}
\end{figure}
